%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% LaTeX book template                           %%
%% Author:  Amber Jain (http://amberj.devio.us/) %%
%% License: ISC license                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,11pt]{report}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Source: http://en.wikibooks.org/wiki/LaTeX/Hyperlinks %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage[english]{babel}

\usepackage{listings}
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}



\newcommand\blfootnote[1]{%
	\begingroup
	\renewcommand\thefootnote{}\footnote{#1}%
	\addtocounter{footnote}{-1}%
	\endgroup
}


\graphicspath{ {../object_property_topic_maps/} }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Chapter quote at the start of chapter        %
% Source: http://tex.stackexchange.com/a/53380 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\makeatletter
\renewcommand{\@chapapp}{}% Not necessary...
\newenvironment{chapquote}[2][2em]
  {\setlength{\@tempdima}{#1}%
   \def\chapquote@author{#2}%
   \parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
   \itshape}
  {\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
\makeatother

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% First page of book which contains 'stuff' like: %
%  - Book title, subtitle                         %
%  - Book author name                             %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Book's title and subtitle
\title{\Huge \textbf{CSE 6708 - Semantic Web} \\
	 \huge Assignment 2 \\
	 \normalsize Report on Paper Presentation \\
	 \normalsize \textbf{Paper Name} Source Code Plagiarism Detection Method Using Protégé Built Ontologies
}
% Author
\author{\textsc{Samidhya Sarker} \\ Student No. 1018052049 \\ Group-2}


\begin{document}

%\frontmatter
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Auto-generated table of contents, list of figures and list of tables %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\tableofcontents
\listoffigures
\lstlistoflistings
%\listoftables

%\mainmatter

%%%%%%%%%%%
% Preface %
%%%%%%%%%%%

\chapter{Paper Summery}

\chapter{Analysis of References present in Given Paper}

\section{List of Citation}


\begin{enumerate}
    \item M. K. Shenoy, K. C. Shet and U. D.  Acharya. (2012, May). Semantic Plagiarism Detection System Using Ontology Mapping.  Advanced Computing: An International Journal [Online].3(3). \footnote{\url{http://airccse.org/journal/acij/papers/0512 acij06.pdf}} \label{listref1}
    
    \item The Protégé Ontology Editor and Knowledge Acquisition System. \footnote{\url{http://protege.stanford.edu/}} (2013, July 1).  \label{listref2}
    
    \item T. Bray, J. Paoli, C. M. Sperberg-McQueen, E. Maler and F. Yergeau.  (2004, February 4). Extensible Markup Language (XML) 1.0.  W3C Recommendation [Online]. Third Edition.
    \footnote{\url{http://www.w3.org/TR/2004/REC-xml20040204/}} \label{listref3}
    
    \item F. Manola and E. Miller (2004, February 10). RDF Primer. W3C Recommendation [Online]. \footnote{\url{http://www.w3.org/TR/2004/REC-rdfprimer-20040210/}} \label{listref4}
    
    \item S. Harris, A. Seaborne. (2013, March 21).  SPARQL 1.1 Query Language. W3C Recommendation [Online]. Available: \footnote{\url{http://www.w3.org/TR/2013/RECsparql11-query-20130321/}} \label{listref5}
    
    \item J. Bao, D. Calvanese, B. C. Grau, et al.  (2012, December 11). OWL 2 Web Ontology Language.  W3C Recommendation [Online].  Second Edition. \footnote{\url{http://www.w3.org/TR/owl2-overview/}} \label{listref6}
    
    \item E Akin, Object Oriented Programming, Houston: Rice University Publishing House, 2001, pp. 33-34.\label{listref7}
    
    \item S. Kara, O. Alan and O. Sabuncu, “An ontology-based retrieval system using semantic indexing”, Information Systems, vol. 37, no. 4, pp. 294–305, June 2012. \label{listref8}
    
    \item Pseudocode Standards, California Polytechnic State University Website. 
    \footnote{\url{http://users.csc.calpoly.edu/~jdalbey/SW E/pdl\_std.html (2013, July 1)}}\label{listref9}
    
    \item C. Liu, H. Wang, Y. Yu and L. Xu, “Towards Efficient SPARQL Query Processing on RDF Data”, Tsinghua Science \& Technology, vol. 15, no. 6, pp.  613–622, December 2010.\label{listref10}
    
    \item I. Ivan and C. Boja, Metode Statistice in analiza software. Bucharest: ASE Publishing House, 2004, pp. 218-224.  Informatica Economică vol. 17, no. 3/2013\label{listref11}
    
    \item S. Russel and P. Norving, Artificial Intelligence: A Modern Approach (2nd edition). New Jersey: Pearson Education Inc., 2003, pp. 350-352.\label{listref12}
    
    \item P. Durusau, S. Newcomb and R. Barta (2007, November). Topic Maps Reference Model. International Organization for Standardization. \footnote{\url{http://www.isotopicmaps.org/TMRM/TM RM-7.0/tmrm7.pdf}}\label{listref13}
    
    \item D. Newman, T. Baldwin, L. Cavedon and E. Huang, “Visualizing search results and document collections using topic maps”, Web Semantics: Science, Services and Agents on the World Wide Web, vol. 8, no. 2-3, pp 169–175, July 2010.\label{listref14}
    
    \item A. Hatzigaidas, A. Papastergiou, G.  Tryfon and D. Maritsa, “Topic Map Existing Tools: A Brief Review”, in Proc.  The International Conference on Theory and Applications of Mathematics and Informatics, Thessaloniki, Greece, 2004, pp 185-201  \label{listref15}
\end{enumerate}

\section{Classification of Given Citation}

\begin{itemize}
	\item Reference \ref{listref1} is a paper published in an international Journal.
	
	\item Reference \ref{listref2} is the homepage of Protege editor.
	
	\item Reference \ref{listref3} is World Wide Web Consortium (W3C) recommendation of XML. 

	\item Reference \ref{listref4} is World Wide Web Consortium (W3C) primer for RDF.

	\item Reference \ref{listref5} is World Wide Web Consortium (W3C) recommendation for SPARQL.
	
	\item Reference \ref{listref6} is  Wide Web Consortium (W3C) recommendation for OWL. 

	\item Reference \ref{listref7} is a book on OOP.
	 
	\item Reference \ref{listref8} is a Masters thesis from Middle East University (Turkey) on semantic indexing.
	
	\item Reference \ref{listref9} is a dead link to a standard on pseudocode writing. Currently can be found on scribd \footnote{\url{https://www.scribd.com/document/47856615/PSEUDOCODE-STANDARD}}.
	
	\item Reference \ref{listref10} is an IEEE paper on SPARQL Query processing.

	\item Reference \ref{listref11} is an book on Statistical methods in software analysis written in Romanian. 
	
	\item Reference \ref{listref12} is the most widespread book on AI. 
	
	\item Reference \ref{listref13} is the ISO reference model for topic maps. 
	
	\item Reference \ref{listref14}  
	
	\item Reference \ref{listref15}  
	
\end{itemize}

\subsection{Comment}

As we can see that references 3-6, 13 are specifications from W3C, ISO. Reference 2 is a website.
And References 11, 12 are excerpts from books. So, we shall analyze refences 1, 8, 10, 14, 15.

\chapter{Analyis of Citations of Given Paper}

\chapter{Future Work}

\chapter{Appendix}

\end{document}
